---
title: "dplyr"
author: "Ze Li"
date: "2023-09-26"
output: github_document
---

inner join keeps the the same

left join keeps the the same as the 1st has & drops Na in the 2nd; 

right join keeps the the same as the 2nd has & drops Na in the 1st; 

full join keeps everthing; ?=bind_rows

```{r}
library(tidyverse)
```

## PULSE data

```{r}
pulse_df = 
  haven::read_sas("data/public_pulse_data.sas7bdat") |>
  janitor::clean_names() |>
  pivot_longer(
    bdi_score_bl:bdi_score_12m,
    names_to = "visits",
    values_to = "bdi_score",
    names_prefix = "bdi_score_" #delete qianzhui
  ) |>
  mutate(
    visits = replace(visits, visits == "bl", "00m")
  ) 
```

Learning Assessment: In the litters data, the variables `gd0_weight` and `gd18_weight` give the weight of the mother mouse on gestational days 0 and 18. Write a data cleaning chain that retains only `litter_number` and these columns; produces new variables `gd` and `weight`; and makes `gd` a numeric variable taking values `0` and `18` (for the last part, you might want to use recode …). Is this version “tidy”?

Solution

```{r}
litters_df = 
  read_csv("data/FAS_litters.csv") |>
  janitor::clean_names() |>
  select(litter_number,gd0_weight,gd18_weight) |>
  pivot_longer(
    gd0_weight:gd18_weight,
    names_to = "gd",
    values_to = "weight",
    names_prefix = "gd"
  ) |>
  mutate(
    gd = case_match(
      gd,
      "0_weight" ~ 0,
      "18_weight" ~ 18,
    )
  )
```

## bind_rows

## LotR

Import LotR words data

```{r}
fellowship_df = 
  readxl::read_excel("data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(
    movie = "fellowship"
  )

two_towers_df = 
  readxl::read_excel("data/LotR_Words.xlsx", range = "F3:H6") |>
  mutate(
    movie = "two towers"
  )

return_of_the_king_df =
  readxl::read_excel("data/LotR_Words.xlsx", range = "J3:L6") |>
  mutate(
    movie = "return of the king"
  )

lotr_df = 
  bind_rows(fellowship_df,two_towers_df,return_of_the_king_df) |>
  janitor::clean_names() |>
  pivot_longer(
    male:female,
    names_to = "gender",
    values_to = "word"
  ) |>
  relocate(movie)
```


